Allocation Removal by Partial Evaluation in a Tracing JIT

### 2011-01-11 talk/pepm2011/presentation/talk.tex
fixes and a small addition
Fix typo.

\begin{frame}
  \frametitle{Tracing JITs}
  \begin{itemize}
      \item VM contains both an interpreter and the tracing JIT compiler
      \item JIT works by observing and logging what the interpreter does
      \item for interesting, commonly executed code paths
      \item produces a linear list of operations (trace)
      \item trace is optimized turned into machine code
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Tracing JIT: Advantages}
  \begin{itemize}
      \item Traces are interesting linear pieces of code
      \item most of the time correspond to loops
      \item everything called in the trace is inlined
      \item can perform good optimizations on the loop
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Optimizing the Heap Operations in a Trace}
  \begin{itemize}
      \item Contribution of our paper
      \item A simple, efficient and effective optimization of heap operations in a trace
      \item using online partial evaluation
      \item fully implemented an in use in large-scale interpreters
  \end{itemize}
  \pause
  \begin{block}{Ingredients}
      \begin{itemize}
          \item a slightly simplified model for objects on the heap
          \item operational semantics of trace operations that manipulate the heap
          \item optimization rules for those operations
      \end{itemize}
  \end{block}
\end{frame}

@@

\begin{frame}[containsverbatim]
  \frametitle{Optimized Example Trace}
  Trace of \texttt{x = a + b; y = x + c}:
\begin{alltt}
guard_class(a, Integer)
guard_class(b, Integer)
i1 = get(a, intval)
i2 = get(b, intval)
i3 = int_add(i1, i2)
\sout{x = new(Integer)}
\sout{set(x, intval, i3)}
\sout{guard_class(x, Integer)}
guard_class(c, Integer)
\sout{i4 = get(x, intval)}
i5 = get(c, intval)
i6 = int_add(i4, \emph{i3})
y = new(Integer)
set(y, intval, i6)
\end{alltt}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Tracing JITs}
  \begin{itemize}
      \item VM contains both an interpreter and the tracing JIT compiler
      \item JIT works by observing and logging what the interpreter does
      \item for interesting, commonly executed code paths
      \item produces a linear list of operations (trace)
      \item trace is optimized and then turned into machine code
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Tracing JIT: Advantages}
  \begin{itemize}
      \item Traces are interesting linear pieces of code
      \item most of the time correspond to loops
      \item everything called in the trace is inlined
      \item can perform good optimizations on the loop
      \item rarer paths run by the interpreter
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Optimizing the Heap Operations in a Trace}
  \begin{itemize}
      \item Contribution of our paper
      \item A simple, efficient and effective optimization of heap operations in a trace
      \item using online partial evaluation
      \item fully implemented and in use in large-scale interpreters
  \end{itemize}
  \pause
  \begin{block}{Ingredients}
      \begin{itemize}
          \item a slightly simplified model for objects on the heap
          \item operational semantics of trace operations that manipulate the heap
          \item optimization rules for those operations
      \end{itemize}
  \end{block}
\end{frame}

@@

\begin{frame}[containsverbatim]
  \frametitle{Optimized Example Trace}
  Trace of \texttt{x = a + b; y = x + c}:
\begin{alltt}
guard_class(a, Integer)
guard_class(b, Integer)
i1 = get(a, intval)
i2 = get(b, intval)
i3 = int_add(i1, i2)
\sout{x = new(Integer)}
\sout{set(x, intval, i3)}
\sout{guard_class(x, Integer)}
guard_class(c, Integer)
\sout{i4 = get(x, intval)}
i5 = get(c, intval)
i6 = int_add(\emph{i3}, i5)
y = new(Integer)
set(y, intval, i6)
\end{alltt}
\end{frame}
